Precise predictions for same-sign W-boson scattering at the LHC

### 2018-02-27 Draft/scanNLO.tex

These differences are much more evident in differential distributions.
In Fig.~\ref{fig:mjjdyjj_1d_1}, we show the distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and rapidity separation $|\Delta y_{\Pj\Pj}|$.
For large $m_{\Pj\Pj}$ and large $|\Delta y_{\Pj\Pj}|$, as expected, the VBS approximation is performing well and its $s$-channel extension agree with the full calculation within $10\%$ per cent.
% On the other hand, for low invariant and low rapidity separation the the VBS approximation is failing at a level of at least $30\%$.
% In this very same region, the VBS approximation with $s$-channel is good within $10\%$.
This is in contrast with the region  $200 \GeV < m_{\Pj\Pj} < 500 \GeV$ and $2<|\Delta y_{\Pj\Pj}|<2.5$, the discrepancy between the $|t|^2 + |u|^2$ approximation and the full computation goes up to $30\%$.
The inclusion of $s$-channels cures partly the discrepancy in this region.
Still, for the very low $m_{\Pj\Pj}$ a difference of about $5\%$ remains \MP{To be checked the exact numerical value in data}.
This might indicate that interference contributions and/or non-factorisable QCD corrections play a non-negligible role in this phase-space region.

@@

The same positive discrepancy for the $|s|^2 + |t|^2 + |u|^2$ approximation, can be seen in the low transverse-momentum region of the leading jet in the upper plot of Fig.~\ref{fig:mjjdyjj_1d_2}.
In the large invariant mass--small rapidity separation region of Fig.~\ref{fig:ratio2d_NLO}, discrepancies at the level of $15\%$ are present.
This can be traced back to the large $\pt$ and central rapidity region of the leading jets kinematics, shown in Fig.~\ref{fig:mjjdyjj_1d_2}.
For such distributions, despite the $s$-channel inclusion, the discrepancy between the approximated and full result is about $5-10\%$.
In the VBS signal-region the VBS approximation shows a good agreement with the full calculation as documented in details below.

@@

Concerning leptonic observables, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions of the lepton-lepton invariant mass and of the Zeppenfeld variable of the electron, defined as
%
\begin{equation}
%  z_{\Pe^+} = \frac{y_{\Pe^+}-\frac{y_{\Pj_1}+y_{\Pj2}}2}{|y_{\Pj_1}-y_{\Pj_2}|} \,.
  z_{\Pe^+} = \frac{y_{\Pe^+}-\frac{y_{\Pj_1}+y_{\Pj2}}2}{|\Delta y_{jj}|} \,.
  \label{eq:Zeppenfeld}
\end{equation}
%
Analogous definitions will later also be used for the Zeppenfeld variable of the muon and of the third jet.
%
\begin{figure*}[hbt]
\centering
{\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
{\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
\caption{Differential distributions in the lepton-lepton invariant mass (left) and the electron Zeppenfeld variable (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
\label{fig:mjjdyjj_1d_3}
\end{figure*}
%
The {\sc VBFNLO} result for the $e^+\mu^+$ invariant mass agrees rather well with the full curve, obtained from {\sc MoCa\-NLO+Recola}.
The prediction from {\sc Bonsay} is about $10\%$ lower.
The discrepancies are roughly constant over the whole spectrum.
Instead, the right panel of Fig.~\ref{fig:mjjdyjj_1d_3} clearly shows that the Zeppenfeld variable of the positron $z_e$ is strongly affected by the exclusion of $s$-channels, with increasing discrepancy with respect to the full result at large values.
The muon observable $z_{\mu}$ behaves identically to the electron one, $z_e$.

>>>>

These differences are much more evident in differential distributions.
In Fig.~\ref{fig:mjjdyjj_1d_1}, we show the distributions in the di-jet invariant mass $m_{\Pj\Pj}$ and rapidity separation $|\Delta y_{\Pj\Pj}|$.
For large $m_{\Pj\Pj}$ and large $|\Delta y_{\Pj\Pj}|$, as expected, the VBS approximation is performing well and its $s$-channel extension agree with the full calculation within $10\%$ per cent.
% On the other hand, for low invariant and low rapidity separation the the VBS approximation is failing at a level of at least $30\%$.
% In this very same region, the VBS approximation with $s$-channel is good within $10\%$.
This is in contrast with the region  $200 \GeV < m_{\Pj\Pj} < 500 \GeV$ and $2<|\Delta y_{\Pj\Pj}|<2.5$, the discrepancy between the $|t|^2 + |u|^2$ approximation and the full computation goes up to $30\%$.
The inclusion of $s$-channels cures partly the discrepancy in this region.
Still, for the very low $m_{\Pj\Pj}$ a difference of about $8\%$ remains \MP{To be checked the exact numerical value in data}.
This might indicate that interference contributions and/or non-factorisable QCD corrections play a non-negligible role in this phase-space region.

@@

The same positive discrepancy for the $|s|^2 + |t|^2 + |u|^2$ approximation, can be seen in the low transverse-momentum region of the leading jet in the upper plot of Fig.~\ref{fig:mjjdyjj_1d_2}.
In the large invariant mass--small rapidity separation region of Fig.~\ref{fig:ratio2d_NLO}, discrepancies at the level of $15\%$ are present. This can be traced back to the large $\pt$ and central rapidity region of the leading jets kinematics, shown in Fig.~\ref{fig:mjjdyjj_1d_2}.{\bf GP: should think again about it, in the lights of the new high stat Recola results. The discrepancy is no more negative in the large pt region.}
For such distributions, despite the $s$-channel inclusion, the discrepancy between the approximated and full result is about $5-10\%$.
In the VBS signal-region the VBS approximation shows a good agreement with the full calculation as documented in details below.

@@

Concerning leptonic observables, we show in Fig.~\ref{fig:mjjdyjj_1d_3} the distributions of the lepton-lepton invariant mass and of the Zeppenfeld variable of the electron, defined as
%
\begin{equation}
%  z_{\Pe^+} = \frac{y_{\Pe^+}-\frac{y_{\Pj_1}+y_{\Pj2}}2}{|y_{\Pj_1}-y_{\Pj_2}|} \,.
  z_{\Pe^+} = \frac{y_{\Pe^+}-\frac{y_{\Pj_1}+y_{\Pj2}}2}{|\Delta y_{jj}|} \,.
  \label{eq:Zeppenfeld}
\end{equation}
%
Analogous definitions will later also be used for the Zeppenfeld variable of the muon and of the third jet.
%
\begin{figure*}[hbt]
\centering
{\includegraphics[scale=0.35]{figures/scanfigures/mll_nlo.pdf}}
{\includegraphics[scale=0.35]{figures/scanfigures/zel_nlo.pdf}}
\caption{Differential distributions in the lepton-lepton invariant mass (left) and the electron Zeppenfeld variable (right) at NLO QCD \emph{i.e.}\ at order $\mathcal{O}(\alphas\alpha^6)$ for the full computation and two approximations.
The upper plots provide the absolute value for each prediction while the lower plots presents all predictions normalised to {\sc MoCaNLO}+{\sc Recola} which is one of the full predictions.
In addition to the cuts of Sec.~\ref{subsec:inputpar}, the VBS cuts take the values: $m_{\Pj\Pj}>200 \GeV$ and $|\Delta y_{\Pj\Pj}|>2$.} 
\label{fig:mjjdyjj_1d_3}
\end{figure*}
%
The {\sc VBFNLO} result for the $e^+\mu^+$ invariant mass agrees rather well with the full curve, obtained from {\sc MoCa\-NLO+Recola}.
The prediction from {\sc Bonsay} is about $10\%$ lower for $m_{e^+\mu^+}<1200 \GeV$; this discrepancy reaches about $20\%$ in the very high mass region. 
%The discrepancies are roughly constant over the whole spectrum.
Instead, the right panel of Fig.~\ref{fig:mjjdyjj_1d_3} clearly shows that the Zeppenfeld variable of the positron $z_e$ is strongly affected by the exclusion of $s$-channels, with increasing negative discrepancy with respect to the full result at large values (up to $30\%$ for $z_{e^+}>1.2$). Including $s$-channels makes this discrepancy become positive, but smaller than $10\%$ over the whole spectrum.
The muon observable $z_{\mu}$ behaves identically to the electron one, $z_e$.
